### 2018-01-30 submission/manuscript.Rmd
update with new fig1

***Number of OTUs is Dependent on the HiFi DNA Polymerase Used:***
In order to compare the number of OTUs across individuals a Z-score normalization by individual, by cycle number, was employed on the number of OTUs data. After normalization, we identified that there was a HiFi DNA polymerase dependent difference that became more apparent as the depth of sub-sampling increased [Figure 1]. Lower cycle numbers (15-20) resulted in less differences between HiFI DNA polymerase while cycle numbers of 25, 30, and 35 having distinct differences [Figure 1]. All subsampling levels were significantly different only at 35 cycles (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "35x")[, "bh"]) < 0.0001, invisible("<"), invisible("check data"))` 0.0001) [Table S1]. There were differences in HiFi DNA polymerase at 25 and 30 cycles but the sub-sampling depth had to be 5000 or higher (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "30x", sub_sample_level != 1000)[, "bh"]) < 0.05 & max(filter(fs_anova_summary, cycle == "25x", sub_sample_level != 1000)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S1]. Platinum HiFi DNA polymerase was the main driver of the differences observed across all sub-sampling depths at 35 cycles, based on a Tukey post-hoc test (P-value `r ifelse(max(filter(fs_tukey_summary, padj < 0.05)[, "padj"]) < 0.05,  invisible("<"), invisible("check data"))` 0.05) [Table S2].

@@

**Figure 1: Normalized Fecal Number of OTUs.** A) Sub-sampled to 1000 reads. B) Sub-sampled to 5000 reads. C) Sub-sampled to 10000 reads. D) Sub-sampled to 15000 reads. The dotted line represents no change from the mean number of OTUs within that specific individual.

>>>>

***Number of OTUs is Dependent on the HiFi DNA Polymerase Used:***
In order to compare the number of OTUs across individuals a Z-score normalization by individual, by cycle number, was employed on the number of OTUs data. After normalization, we identified that there was a HiFi DNA polymerase dependent difference that was consistent across sub-sampling [Figure 1]. Lower cycle numbers (15-20) tended to result in less differences between HiFI DNA polymerase while cycle numbers of 25, 30, and 35 tended to have more distinct differences [Figure 1]. All subsampling levels were significantly different only at 35 cycles (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "35x")[, "bh"]) < 0.0001, invisible("<"), invisible("check data"))` 0.0001) [Table S1]. There were differences in HiFi DNA polymerase at 25 and 30 cycles but the sub-sampling depth had to be 5000 or higher (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "30x", sub_sample_level != 1000)[, "bh"]) < 0.05 & max(filter(fs_anova_summary, cycle == "25x", sub_sample_level != 1000)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S1]. Platinum HiFi DNA polymerase was the main driver of the differences observed across all sub-sampling depths at 35 cycles, based on a Tukey post-hoc test (P-value `r ifelse(max(filter(fs_tukey_summary, padj < 0.05)[, "padj"]) < 0.05,  invisible("<"), invisible("check data"))` 0.05) [Table S2].

@@

**Figure 1: Normalized Fecal Number of OTUs.** The x-axis represents the different sub-sampling depths used and the y-axis is the normalized within individual number of OTUs. The red line represents the overall mean Z-score normalized number of OTUs for each respective HiFi DNA polymerase. The dashed black line represents the overall Z-score normalized mean number of OTUs.

### 2018-01-30 submission/manuscript.tex
update with new fig1

\textbf{\emph{Number of OTUs is Dependent on the HiFi DNA Polymerase
Used:}} In order to compare the number of OTUs across individuals a
Z-score normalization by individual, by cycle number, was employed on
the number of OTUs data. After normalization, we identified that there
was a HiFi DNA polymerase dependent difference that became more apparent
as the depth of sub-sampling increased {[}Figure 1{]}. Lower cycle
numbers (15-20) resulted in less differences between HiFI DNA polymerase
while cycle numbers of 25, 30, and 35 having distinct differences
{[}Figure 1{]}. All subsampling levels were significantly different only
at 35 cycles (P-value \textless{} 0.0001) {[}Table S1{]}. There were
differences in HiFi DNA polymerase at 25 and 30 cycles but the
sub-sampling depth had to be 5000 or higher (P-value \textless{} 0.05)
{[}Table S1{]}. Platinum HiFi DNA polymerase was the main driver of the
differences observed across all sub-sampling depths at 35 cycles, based
on a Tukey post-hoc test (P-value \textless{} 0.05) {[}Table S2{]}.

@@

\textbf{Figure 1: Normalized Fecal Number of OTUs.} A) Sub-sampled to
1000 reads. B) Sub-sampled to 5000 reads. C) Sub-sampled to 10000 reads.
D) Sub-sampled to 15000 reads. The dotted line represents no change from
the mean number of OTUs within that specific individual.

>>>>

\textbf{\emph{Number of OTUs is Dependent on the HiFi DNA Polymerase
Used:}} In order to compare the number of OTUs across individuals a
Z-score normalization by individual, by cycle number, was employed on
the number of OTUs data. After normalization, we identified that there
was a HiFi DNA polymerase dependent difference that was consistent
across sub-sampling {[}Figure 1{]}. Lower cycle numbers (15-20) tended
to result in less differences between HiFI DNA polymerase while cycle
numbers of 25, 30, and 35 tended to have more distinct differences
{[}Figure 1{]}. All subsampling levels were significantly different only
at 35 cycles (P-value \textless{} 0.0001) {[}Table S1{]}. There were
differences in HiFi DNA polymerase at 25 and 30 cycles but the
sub-sampling depth had to be 5000 or higher (P-value \textless{} 0.05)
{[}Table S1{]}. Platinum HiFi DNA polymerase was the main driver of the
differences observed across all sub-sampling depths at 35 cycles, based
on a Tukey post-hoc test (P-value \textless{} 0.05) {[}Table S2{]}.

@@

\textbf{Figure 1: Normalized Fecal Number of OTUs.} The x-axis
represents the different sub-sampling depths used and the y-axis is the
normalized within individual number of OTUs. The red line represents the
overall mean Z-score normalized number of OTUs for each respective HiFi
DNA polymerase. The dashed black line represents the overall Z-score
normalized mean number of OTUs.
